Inference of Bifurcations with Differentiable Continuation

### 2021-02-23 docs/article.tex

The algorithm also takes hyperparameters $\beta$ which will contain arclength step sizes, eigenvalue and Newton solver options and unsupervised correction factor $\lambda$. The adaptive hyperparameter update is done by \texttt{updateHyperparameters} and should depend on the current solutions $\Omega$ and the targets $\targets$. The step sizes and solver options should adapt to the expected space of the solutions $\Omega$ so that the waiting time between iterations is minimised. The unsupervised correction factor $\lambda$ should be large when there are no predicted bifurcations and decrease as the number of predicted bifurcations approaches the number of targets.

>>>>

The algorithm also takes hyperparameters $\beta$ which will contain arclength step sizes, eigenvalue and Newton solver options and unsupervised correction factor $\lambda$. The adaptive hyperparameter update is done by \texttt{updateHyperparameters} and should depend on the current solutions $\partial S$ and the targets $\targets$. The step sizes and solver options should adapt to the expected space of the solutions $\partial S$ so that the waiting time between iterations is minimised. The unsupervised correction factor $\lambda$ should be large when there are no predicted bifurcations and decrease as the number of predicted bifurcations approaches the number of targets.
